---
title: "Chapter 3 - report exercise"
output: html_document
date: "2023-03-15"
---

First step is to read in the file with the cleaned data.
In this case i am going to name it "DatabaseS1_cleaned"
```{r}
DatabaseS1_cleaned <-read.csv("C:/Users/andri/Desktop/UNIBE/Geographie/Aufbaustudium/Jahr 2/Semester 4/AGDS/chapter 3/Database_S1_cleaned_CSV.csv",header=TRUE,sep=";")
DatabaseS1_cleaned
```
Now I want to aggregate the data. For this step I take the mean of each experiment for the variables "mean.ambient.CO2" and "mean.increased.CO2".To lose no data, I am gonna make a new table, which only contains the aggregated mean values for each of the two variables.
```{r}
DatabaseS1_aggregated <- DatabaseS1_cleaned[,6:7]
DatabaseS1_aggregated$Experiment<-DatabaseS1_cleaned[,1]

DatabaseS1_aggregated
```

```{r}
library(tidyverse)
```

```{r}
#to aggregate for ambient Co2
DatabaseS1_aggregated_meana <- DatabaseS1_aggregated |>  
  group_by(Experiment) |> 
  summarise(mean.ambient.CO2..f.C.m..2.
 = mean(mean.ambient.CO2..f.C.m..2.))
 
#to aggregate for increased Co2
DatabaseS1_aggregated_meani <- DatabaseS1_aggregated |>  
  group_by(Experiment) |> 
  summarise(mean.increased.CO2..f.C.m..2.
 = mean(mean.increased.CO2..f.C.m..2.))

#adding the two aggregated tables together
DatabaseS1_aggregated_mean <- DatabaseS1_aggregated_meani[,1]

DatabaseS1_aggregated_mean$mean.increased.CO2..f.C.m..2.<-DatabaseS1_aggregated_meani[,2]
DatabaseS1_aggregated_mean$mean.ambient.CO2..f.C.m..2.<-DatabaseS1_aggregated_meana[,2]
```

```{r}
#controll if "<tibble> refers to a number or if it is an error
DatabaseS1_aggregated_mean[1,2]*DatabaseS1_aggregated_mean[1,3]

DatabaseS1_aggregated_meana[1,2]*DatabaseS1_aggregated_meani[1,2]
#gives same result -> perfectly fine
```
log response ratio of each experiment by using the formula
ln(x elevated/x ambient)
```{r}
vectorlog=data.frame()
vectorlog$logresponse

for (x in seq(1,53)){
  vectorlog[x,1]<-log(DatabaseS1_aggregated_mean[x,2]/DatabaseS1_aggregated_mean[x,3])
}

vectorlog
DatabaseS1_aggregated_mean$log_response<-vectorlog
DatabaseS1_aggregated_mean
```
````{r}
#controll on wheater these are possible results or not... but seems to be legit
DatabaseS1_aggregated_mean[1,4]*1
DatabaseS1_aggregated_mean[2,4]*1
DatabaseS1_aggregated_mean[3,4]*1
DatabaseS1_aggregated_mean[4,4]*1

```

group by years/time which the experiment went on
group 1: 0-3 years
group 2: 3-6 years
group 3: 6< years
I am gonna use the same procedure as above. That means firstly I am gonna create a new table with the 3 variables i need.
```{r}
DatabaseS1_aggregated_time <- DatabaseS1_cleaned[,5:7]
?dplyr
```

```{r}
#liste mit den jahren 0-3
list0_3<-DatabaseS1_aggregated_time|>
  dplyr::arrange(Time..years.)|>
  dplyr::filter(Time..years.<=3)
logresponse1=log(sum(list0_3[,2]
)/sum(list0_3[,3]))
logresponse1

#liste mit den jahren 3-6
list3_6<-DatabaseS1_aggregated_time|>
  dplyr::arrange(Time..years.)|>
  dplyr::filter(Time..years.>3 & Time..years.<=6)
logresponse2=log(sum(list3_6[,2]
)/sum(list3_6[,3]))
logresponse2
#liste mit den jahren 6+
list6mehr<-DatabaseS1_aggregated_time|>
  dplyr::arrange(Time..years.)|>
  dplyr::filter(Time..years.<=3)

logresponse3=log(sum(list6mehr[,2]
)/sum(list6mehr[,3]))
logresponse3
logresponse=c(logresponse1,logresponse2,logresponse3)
logresponse
```

