```{r}
#d in the data as a table
half_hourly_fluxes <- read.csv("/Users/andri/Desktop/UNIBE/Geographie/Aufbaustudium/Jahr 2/Semester 4/AGDS/AGDS_report_AndriWidmer/report exercises/chapter 8/df_for_stepwise_regression.csv",header=TRUE,sep=",")
```

```{r}
library(tidyverse)
library(ggplot2)
```
# the aim is to perform a forward linear regression. This method contains 5 steps which are described in the script. Our Y-variable is the GPP. The GPP will be modelled, while all other variables take the role as predictors.
```{r}
linmod1 <- lm(GPP_NT_VUT_REF~TA_F,data = half_hourly_fluxes)
linmod2 <- lm(GPP_NT_VUT_REF~SW_IN_F,data = half_hourly_fluxes)
linmod3 <- lm(GPP_NT_VUT_REF~LW_IN_F,data = half_hourly_fluxes)
linmod4 <- lm(GPP_NT_VUT_REF~VPD_F,data = half_hourly_fluxes)
linmod5 <- lm(GPP_NT_VUT_REF~PA_F,data = half_hourly_fluxes)
linmod6 <- lm(GPP_NT_VUT_REF~P_F,data = half_hourly_fluxes)
linmod7 <- lm(GPP_NT_VUT_REF~WS_F,data = half_hourly_fluxes)
linmod8 <- lm(GPP_NT_VUT_REF~TA_F_MDS,data = half_hourly_fluxes)
linmod9 <- lm(GPP_NT_VUT_REF~LW_IN_F_MDS,data = half_hourly_fluxes)
linmod10 <- lm(GPP_NT_VUT_REF~VPD_F_MDS,data = half_hourly_fluxes)
linmod11 <- lm(GPP_NT_VUT_REF~CO2_F_MDS,data = half_hourly_fluxes)
linmod12 <- lm(GPP_NT_VUT_REF~PPFD_IN,data = half_hourly_fluxes)
linmod13 <- lm(GPP_NT_VUT_REF~USTAR,data = half_hourly_fluxes)
summary(linmod1)
summary(linmod2)
summary(linmod3)
summary(linmod4)
summary(linmod5)
summary(linmod6)
summary(linmod7)
summary(linmod8)
summary(linmod9)
summary(linmod10)
summary(linmod11)
summary(linmod12)
summary(linmod13)
```
#with the variable PPFD_IN we get the highest R^2. But there are also a lot of datapoints missing. Abotu 6137 were deleted. Compared to the whole dataset (aproximately 23000 points), this is nearly a quarter. Second highest R^2 got the variable SW_IN_F. It was 0.4306 and 2403 points were deleted. I guess this is a more representative variable to continue with. 
```{r}
ggplot(data=half_hourly_fluxes,aes(x=SW_IN_F,y=GPP_NT_VUT_REF))+geom_point()+geom_smooth(formula= y~x,method="lm",color="red")
```
#This figure shows the two variables SW_IN_F and GPP_NT_VUT_REF. On the X-axis there is the SW_IN_F (predictor) and on the Y-axis there is the GPP. The red line is the regression line.

```{r}
extractAIC(linmod2)
```
#computing the AIC for the regression of GPP and SW_IN_F.

#Now the first to the third step of the forward regression are completed. For the second part of exercise 8 I also have to solve step four and five. I will add an extra varibale to all regression modells above. When the AIC of the modell with the highest R^2 then gets higher than the one of the modell with one predictor, I will continue to add more predictors. In case AIC gets lower, I will stop adding more predictors.

#I will try to solve the problem with the "step" function of the "stats" package. This creates automatically, depending on the aim, either a forward, backward or mixed stepping regression.
```{r}
library(stats)
```

```{r}
half_hourly_fluxes_for_sfreg=half_hourly_fluxes #creating new table for easier use
half_hourly_fluxes_for_sfreg<- subset(half_hourly_fluxes_for_sfreg, select = -siteid)#deleting sites
half_hourly_fluxes_for_sfreg<- subset(half_hourly_fluxes_for_sfreg, select = -TIMESTAMP)#deleting timestamp
half_hourly_fluxes_for_sfreg<- subset(half_hourly_fluxes_for_sfreg, select = -LW_IN_F_MDS)#deleting the variable LW_IN_F_MDS because a lot of data is missing (see below).
```

```{r}
plot(half_hourly_fluxes[,12])#therefore delete this variable (LW_IN_F_MDS) because of the dataholes. Done in the statement above
```


```{r}
library(tidyr)
half_hourly_fluxes_for_sfreg_noNA<-half_hourly_fluxes_for_sfreg %>% drop_na()  
```


```{r}
linmod_modell=lm(GPP_NT_VUT_REF~1,data = half_hourly_fluxes_for_sfreg_noNA)
#start with only one intersect

linmod_fitAll=lm(GPP_NT_VUT_REF~.,data=half_hourly_fluxes_for_sfreg_noNA)#scope= maximum of variables to use

```

```{r}
step(linmod_modell,direction="forward",scope=formula(linmod_fitAll),steps=1000)
```
#The AIC decreases pretty fast at the beginning and then goes down more slowly after certain steps. The most accurate regression modell get an AIC score of 22769. It started at 36501.08. The modell which is the best contain the following variables: GPP_NT_VUT_REF ~ PPFD_IN + LW_IN_F + VPD_F + TA_F_MDS + SW_IN_F + P_F + WS_F + USTAR + CO2_F_MDS + PA_F + VPD_F_MDS.

```{r}
a=lm(GPP_NT_VUT_REF ~ PPFD_IN + LW_IN_F + VPD_F + TA_F_MDS + SW_IN_F + P_F + WS_F + USTAR + CO2_F_MDS + PA_F + VPD_F_MDS,data=half_hourly_fluxes_for_sfreg_noNA)
summary(a)
```
#Overall the Multiple R^2 is 0.5896. The p-value is quite small. This modell can therefore be seen as statistically relevant. 
